There are no small Advantages: Reinforcement learning in near continuous time with Deep RelAtive Mixture of Advantages

### 2018-12-06 paper/icml_drau/icml_drau.tex
Biblio for paper

%\printAffiliationsAndNotice{}  % leave blank if no need to mention equal contribution
\printAffiliationsAndNotice{\icmlEqualContribution} % otherwise use the standard text.

@@

\section{Related work}
\label{sec:related}

\section{Continuous reinforcement learning and scaling problems}
\label{sec:continous}
In the following section, a restrictive framework for near continuous
time reinforcement learning is introduced, and the main challenges of this
setup are explained. \RKC{This is not what we want to write: we want to explain
why current reinforcement learning practices are ill suited for this framework}

@@

Under a deterministic policy $\pi$, one can define the \emph{state value function} $V^\pi(s)$
and \emph{state action value function} $Q^\pi(s, a)$ as
\begin{align}

\end{align}

>>>>

%\printAffiliationsAndNotice{}  % leave blank if no need to mention equal contribution
%\printAffiliationsAndNotice{\icmlEqualContribution} % otherwise use the standard text.

@@

\section{Related work}
\label{sec:related}
\cite{adv_upd}
\cite{adv_learn}
\cite{dueling_nets}

\section{Continuous reinforcement learning and scaling problems}
\label{sec:continous}
In the following section, a restricted framework for near continuous
time reinforcement learning is introduced, and the main challenges of this
setup are explained. \RKC{This is not what we want to write: we want to explain
why current reinforcement learning practices are ill suited for this framework}

@@

Under a deterministic policy $\pi$, one can define the $\gamma$ discounted
\emph{state value function} $V^\pi(s)$ and \emph{state action value function}
$Q^\pi(s, a)$\footnote{
	The values of $V^\pi$ and $Q^\pi$ are derived as discretization of e.g.
	$V^\pi_\text{cont}(s) = \E\left[\int\limits_0^\infty \gamma^t \reward(s_t, \pi(s_t)) dt \mid s_0 = s\right]$.
}as
\begin{align}
	V^\pi(s) &= \E\left[
		\sum\limits_{k=0}^\infty \gamma^{k\deltat}
		r_{k \deltat} \mid s_0 = s
	\right]\\
	Q^\pi(s, a) &= \E\left[
		\sum\limits_{k=0}^\infty \gamma^{k\deltat}
		r_{k \deltat} \mid s_0 = s, a_0 = a
	\right].
\end{align}
Both $V^\pi$ and $Q^\pi$ verify Bellman equations, e.g.
\begin{align}
	V^\pi(s) = \reward(s, \pi(s)) \deltat + \gamma^{\deltat} \E_{s_{t+\deltat}\mid s_t=s} V^\pi(s_{t+\deltat}).
\end{align}

\subsection{Scaling problems}
